\textcolor{red}{Robot Team II: Electric Boogaloo}

### 2023-12-26 paper/paper.tex
updated paper and added some figures

\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Robot Team II: Electric Boogaloo}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
% \Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{} and David J. Lary $^{1,\ddagger}$\orcidB{}}
\Author{John Waczak\orcidA{} and David J. Lary\orcidB{}}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{John Waczak and David J. Lary}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Waczak, J.; Lary, D.J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
  Hanson Center for Space Sciences, University of Texas at Dallas, Richardson,
  TX 75080, USA;}

% $^{1}$ \quad John.Waczak@utdallas.edu\\
% $^{2}$ \quad David.Lary@utdallas.edu}

% Contact information of the corresponding author
\corres{Correspondence: John.Waczak@utdallas.edu}

% Current address and/or shared authorship
%\firstnote{} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Fill this out last}

% Keywords
\keyword{Remote Sensing; hyperspectral image; georectification; machine learning}

@@

\subsection{Importance / Human Impact}
oil spill response, contaminated water, environmental surveys, algal blooms,
agriculture, land monitoring, air quality, etc...

paper using spectral indices for water quality assesment \cite{SpectralIndexWaterQuality}

\subsection{Hyperspectral Imaging and Remote Sensing}
paper creating new spectral index for wheat rust \cite{SpectralIndexWheat} \\ 
overview of NDVI \cite{SpectralIndexNDVI} \\ 
paper using spectral indices for desertification \cite{SpectralIndexDesertification}

\subsubsection{HSI sattelite systems}
\subsubsection{HSI drone systems}
\subsubsection{Machine Learning using HSI}
add Xiao He reference here \cite{yu2021pm2}

\subsection{In-situ Measurements / Robot Teams}
\subsubsection{Meteorology}
\subsubsection{Atmospheric Sensing}
add in reference to our AQ sensor network

\subsection{Julia Programming Language}
\subsubsection{scientific computing}
\subsubsection{differentiable programming ($\partial P$)}
\subsubsection{MLJ}
discuss general \textit{learning network} framework and utilization of
Directed Acyclic Graphs for pipeline construction

basic overview of MLJ as a Julia package \cite{MLJ1}\\

detailed description of \textit{learning networks} \cite{MLJ2}

\section{Materials and Methods}
\subsection{Autonomous Collection and Processing of Hyperspectral Images}

website for alta x \cite{freeflyAltaX}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/radiance.eps}
\caption{Spectral Radiance collected from a single pixel of the HSI.\label{radiancePlot}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/solar_irradiance.eps}
\caption{Downwelling Irradiance captured via an upward facing spectrometer.\label{irradiancePlot}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/spectra/reflectance_rainbow.eps}
\caption{Single pixel reflectance spectrum created by combining \ref{radiancePlot} with \ref{irradiancePlot}.\label{radiancePlot}}
\end{figure}

\begin{equation}
    R = \pi \frac{L}{E}
\end{equation}

\subsection{Georectification}
paper by Muller \cite{GeorectificationMuller} \\ 
paper by Baumker \cite{GeorectificationBaumker} \\ 
paper by Mostafa \cite{GeorectificationMostafa} \\

NOTE: need to double check \cite{GeorectificationMuller} for convention used ($\Phi$ vs $\phi$)

Heading correction due to longitude deviation in UTM system: 
\begin{equation}
    \kappa_{\text{geodetic}} = \kappa_{\text{geographic}}-\tan^{-1}\left( \sin\Phi \tan(\lambda-\lambda_{cm}) \right)
\end{equation}

scale factor: 
\begin{equation}
    s = \frac{z_{\text{sensor}}-z_{\text{ground}}}{f}
\end{equation}

\begin{equation}
    \begin{pmatrix}
    x \\ y \\ z
    \end{pmatrix}_{\text{Object}}^{\text{UTM}} = 
    f_{\text{geo}}^{\text{UTM}}\begin{pmatrix}
    \lambda \\ 
    \Phi \\ 
    z
    \end{pmatrix}_{\text{GPS}}^{\text{geo}} + sT_{\text{IMU}}^{\text{UTM}}R_{\text{sensor}}^{\text{IMU}}(\kappa, \phi, \omega)\begin{pmatrix}
    0 \\ 
    y_i \\ 
    f
    \end{pmatrix}_{\text{object}}^{\text{sensor}}
\end{equation}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/georectification/georectification.eps}
\caption{Diagram of .\label{georectification1}}
\end{figure}

\subsection{In-situ Data Collection via Robotic Sentinels}

autonomous boat website \cite{Otter}

\subsubsection{data collection process}
\subsubsection{Data Collocation}

\subsubsection{CO}
\subsubsection{CDOM}
\subsubsection{HDO}
\subsubsection{$Na^{+}$}
\subsubsection{$Ca^{2+}$}
\subsubsection{Other Targets}

\subsubsection{Feature Engineering with Remote Sensing Indices}
include discussion of PCA as well as Standardization

\subsection{Exploratory Data Analysis}
\subsubsection{Variable Correlations}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/target_cor.png}
\caption{Correlation Matrix for Target variables measured by the boat.\label{target_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/radiance_cor.png}
\caption{Correlation Matrix for Radiance measurements versus Target Variables.\label{rad_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/reflectance_cor.png}
\caption{Correlation Matrix for Reflectance measurements versus Target Variables.\label{ref_cor}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/correlation/derived_cor.png}
\caption{Correlation Matrix for derived measurements versus Target Variables.\label{derived_cor}}
\end{figure}

\subsubsection{Unsupervised Classification}
\begin{figure}[H]
\includegraphics[width=11 cm]{images/unsupervised/clustering.png}
\caption{Unsupervised clustering of hyper-spectral image data using the K-means algorithm.\label{clustering}}
\end{figure}

\subsection{Machine Learning}

\subsubsection{Machine Learning Models}
include Linear Models, Neural Networks, Decision Trees, Bagging, Boosting, and Stacking\\

The field of Machine Learning has seen the invention of a plethora of models able to perform inference for regression tasks. Naturally, this leads to the challenge of evaluating which model is best for a given problem. In 1992 David Wolpert developed the notion of Stacked Generalization to divorce arbitrary human choice from the model selection process. [1] The key idea is as follows: fit an instance of each model compatible with your dataset. Each model learns different features of the data so that an adjudicating model (called the super-learner) can then be trained to map the predictions from each individual learner to a final output prediction. This is incredibly easy to accomplish in the Julia programming language via the MLJ machine learning framework [2]. We train a variety of learners including artificial neural networks, bagged decision trees, boosted decision trees, polynomial regressors, quantile regressors, LASSO regressors, and K-nearest-neighbors regressors. To ensure proper data hygiene, individual learners are first trained on separate cross validation folds so as not to bias the super-learner. After training the super-learner, each individual model is then trained on the full dataset to produce the best possible model.

paper on stacking \cite{ModelStacking}

\subsection{Model Analysis}
aleatoric and epistemic uncertainty

The black-box nature most machine learning methods makes it difficult to consider how errors propagate through a trained model during the inference process. For many problems such as image classification this is not an issue, however, in physical sensing error considerations are vital to establish detection limits and prediction confidence. Typically, there are three considerations we must make: measurement uncertainty– how much we can trust our model’s inputs, measurement representativeness– how well each data point represents data within a local neighborhood, and model error– how far the prediction is from the true value. Machine learning models are typically trained to minimize the model error. The Julia programming language makes it possible to handle all three.

To address measurement uncertainty, we take advantage of Julia’s advanced automatic differentiation capabilities to enable differentiable programming (∂P). This means that we can take derivatives of our trained ML model with respect to each input feature to perform a sensitivity analysis. The final output uncertainty is then given via linear error propagation theory. [5]

Measurement representativeness can be trickier to handle. For example, in fluids it is common for two species to form a mixing layer that presents as a sharp discontinuity in measurement values. To quantify the degree to which neighboring points diverge we compute the average deviation across input measurements in a neighborhood around each data sample. This information can then be presented with model outputs to identify the regions where our model is valid. Similarly for ensemble ML models we compute the prediction deviation across all base learners to identify the representativeness of a data sample. Inputs that cause a large spread in base learner predictions indicate low representativeness in the training set. This analysis can then be used to plan further data collection missions that minimize time spent collecting data we have already present in our models.

\subsubsection{Uncertainty Propagation via ($\partial P$)}

\subsubsection{Feature Ranking via SHAP values}

shape value paper used in ShapML.jl \cite{SHAPvalues1}

\subsubsection{Data Representativeness}
i.e. the average deviation across pixels used average during collocation process.
Also, we can look at relative disagreement between model predictions in bagged ensemble.

\section{Results}
\subsection{CO}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/CO_dataMap.png}
\caption{Target distribution of CO at Scotty's Ranch.\label{CO_targetMap}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/CO_train-test_hist.png}
\caption{Stratified train-test split for CO.\label{CO_trainTestHist}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{images/CO/rfr_CO_qq.png}
\caption{Quantile-Quantile plot for CO random forest fit. \label{CO_trainTestHist}}
\end{figure}

\begin{figure}[H]
    \begin{adjustwidth}{-\extralength}{0cm}
    \centering
    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_scatter.png}}\qquad
    \subfigure{\includegraphics[width=0.5\textwidth]{images/CO/rfr_CO_qq.png}}
    \end{adjustwidth}
    \caption{(\textbf{a}) Scatterplot for the trained random forest Crudo Oil model. (\textbf{b}) Quantile-Quantile plot for the same fit.}
    \label{CO_fitresult}
\end{figure}

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{images/CO/rfr_CO_featureImportance.png}
    \caption{Ranked feature importance for Crude Oil. Importance is determined via mean absolute SHAP value. \label{CO_shapely}}
\end{figure}

\section{Discussion}
\subsection{For-deployment Models}
\subsubsection{Random Forests}

\subsection{Limitations}
discuss viewing geometry and time of day

\subsection{Extensions and Future Work}
\subsubsection{Physics-informed machine learning}
\subsubsection{Data Augmentation}

\section{Conclusions}

@@

%=====================================
% References, variant A: external bibliography
% =====================================
\bibliography{references}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{\textcolor{red}{Robot Team II: Electric Boogaloo}}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-4265-9543} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{John Waczak$^{\dagger}$\orcidA{}, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, David Schaefer, David J. Lary, $^{\dagger}$\orcidB{}*}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Waczak, J.; Lary, D.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA\
}

% Contact information of the corresponding author
\corres{Correspondence: David.Lary@utdallas.edu} %; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship

% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{\textcolor{red}{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}}

% Keywords
\keyword{\textcolor{red}{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}}

@@

Remote sensing data products

Hyper-spectral imagery

Launched and soon-to-be-launched HSI satellites

Generation of in-situe reference measurements for the calibration of remote sensing data products

Drone based applications of hyper-spectral imagers

Autonomous robotic teams (cite our previous paper)

Overview of what we demonstrate here...

%The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

\subsection{Autonomous Robotic Team}
\subsubsection{Autonomous Boat: In-situ Sensing}
\subsubsection{Autonomous Drone: Rapid Hyperspectral Imaging}

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/annotated-drone.pdf}
\caption{These are the components of the drone. \label{fig:drone-components}}
\end{figure}

\subsection{Data Collection}
\subsection{Georectification of Hyperspectral Imagery}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{paper/figures/materials-and-methods/pipeline-figure-2.pdf}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig:hsi-pipeline}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{paper/figures/materials-and-methods/HyperSpectralInfoGraphic.pdf}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig:hsi-infographic}}
\end{figure}

\subsection{Machine Learning}
\subsubsection{Data Pre-processing and Feature Generation}
Add a table of the Features we used here...
\subsubsection{Models Employed}
Discuss random forests
\subsubsection{Hyperparameter Optimization}
Discuss the parameters we optimize and the evaluation strategy using 10-fold cross validation.

\subsection{Uncertainty Quantification via Conformal Prediction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Modeling Results}

\begin{table}[H] 
\caption{This is a table caption.\label{tab:fit-results}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCCCCC}
\toprule
\textbf{Target (units)}	& \textbf{$\text{R}^2$}	& \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty (90\% CI)} & \textbf{Empirical Coverage (\%)}\\
\midrule
$\mathrm{Na}^+$     & 0.964 $\pm$ 0.006 & 8.10 $\pm$ 0.68 & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
Dissolved Oxygen    & 0.958 $\pm$ 0.005 & 0.119 $\pm$  & 5.10 $\pm$ 0.26 & 11.7 & 88.5 \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Mapping}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data \textsuperscript{1}\\
\bottomrule
\end{tabularx}
\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
			  	                   & Data			& Data			& Data\\
			             	      & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
			  	                  & Data			& Data			& Data\\
			             	     & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
                  \midrule
\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{* Tables may have a footer.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

@@

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}
